{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2023-10-03 superspace.tex
Small fixes to Sec. 3.2

We have\footnote{Here we use Campbell-Baker-Hausdorff expansion $e^{A}e^{B} = e^{A + B - \frac{1}{2}[A, B] + ...}$ where the terms that follow all contain commutators of the first commutator  $[A, B] $ and the operators $A$ and $B$.}

@@

&& - \frac{1}{2}[ia^\nu P_\nu + i\alpha^BQ_B + i\bar{\alpha}_{\dot{B}}\bar{Q}^{\dot{B}}, iz^\pi K_\pi] + …)

@@

&=&2(\alpha^B\bar{\theta}^{\dot{C}}\sigma^\mu_{B\dot{C}} + \bar{\alpha}^{\dot{C}}\theta^A\sigma^\mu_{A\dot{C}})P_\mu

@@

-\frac{1}{2}[~,~]&=&-(\alpha^A\sigma^\mu{}_{A\dot{A}}\bar{\theta}^{\dot{A}} -\theta^A\sigma^\mu{}_{A\dot{A}}\bar{\alpha}^{\dot{A}})P_\mu.

@@

The commutator is proportional with $P_\mu$, and will therefore commute with all operators, in particular the higher terms in the Campbell-Baker-Hausdorff expansion, meaning that the series reduces to

@@

&=& \exp[i(x^\mu + a^\mu+ i\alpha^A\sigma^\mu_{A\dot{A}}\bar{\theta}^{\dot{A}} - i\theta^A\sigma^\mu_{A\dot{A}}\bar{\alpha}^{\dot{A}})P_\mu + i(\theta^A+\alpha^A)Q_A + i(\bar{\theta}_{\dot{A}}+\bar{\alpha}_{\dot{A}})\bar{Q}^{\dot{A}}].

@@

(x^\mu, \theta^A, \bar{\theta}_{\dot{A}}) \to  (x^\mu + a^\mu -i\alpha^A\sigma^\mu_{A\dot{A}}\bar{\theta}^{\dot{A}} + i\theta^A\sigma^\mu_{A\dot{A}}\bar{\alpha}^{\dot{A}}, \theta^A + \alpha^A, \bar{\theta}_{\dot{A}} + \bar{\alpha}_{\dot{A}}).

@@

f(x^\mu, \theta^A, \bar{\theta}_{\dot{A}},a^\mu, \alpha^A, \bar{\alpha}_{\dot{A}}) =  (x^\mu + a^\mu -i\alpha^A\sigma^\mu{}_{A\dot{A}}\bar{\theta}^{\dot{A}} + i\theta^A\sigma^\mu{}_{A\dot{A}}\bar{\alpha}^{\dot{A}}, \theta^A + \alpha^A, \bar{\theta}_{\dot{A}} + \bar{\alpha}_{\dot{A}}).

@@

As a crucial by-product we can now write down a differential representation for the supersymmetry generators by applying the standard expression for the generators $X_i$ of a Lie algebra, given the composition functions $f_\pi$:
\[X_j = \frac{\partial f_\pi}{\partial a_j}\frac{\partial}{\partial z_\pi},\]
which gives us:\footnote{We define the generators $X_i$ as $iP_\mu$, $iQ_A$ and $iQ_B$ respectively. Again, this is in order to end up with hermitian instead of anti-hermitian generators.}
\begin{eqnarray}
P_\mu &=& -i\partial_\mu \label{eq:diffrepP},\\
iQ_A &=& -i(\sigma^\mu\bar{\theta})_A\partial_\mu +\partial_A,\\
i\bar{Q}^{\dot{A}} &=& -i(\bar{\sigma}^\mu \theta)^{\dot{A}}\partial_\mu +\partial^{\dot{A}}.
\label{eq:diffrepQbar}
\end{eqnarray}

>>>>

We have\footnote{Here we use Campbell-Baker-Hausdorff expansion $e^{A}e^{B} = e^{A + B + \frac{1}{2}[A, B] + ...}$ where the terms that follow all contain commutators of the first commutator  $[A, B] $ and the operators $A$ and $B$.}

@@

&& + \frac{1}{2}[ia^\nu P_\nu + i\alpha^BQ_B + i\bar{\alpha}_{\dot{B}}\bar{Q}^{\dot{B}}, iz^\pi K_\pi] + …)

@@

&=&2(\alpha^B\bar{\theta}^{\dot{C}}\sigma^\mu_{B\dot{C}} + \bar{\alpha}^{\dot{C}}\theta^A\sigma^\mu_{A\dot{C}})P_\mu .

@@

\frac{1}{2}[~,~]&=&(\alpha^A\sigma^\mu{}_{A\dot{A}}\bar{\theta}^{\dot{A}} -\theta^A\sigma^\mu{}_{A\dot{A}}\bar{\alpha}^{\dot{A}})P_\mu.

@@

The commutator is proportional with $P_\mu$, and will therefore commute with all the operators in the problem, in particular the higher terms in the Campbell-Baker-Hausdorff expansion, meaning that the series reduces to

@@

&=& \exp[i(x^\mu + a^\mu - i\alpha^A\sigma^\mu_{A\dot{A}}\bar{\theta}^{\dot{A}} + i\theta^A\sigma^\mu_{A\dot{A}}\bar{\alpha}^{\dot{A}})P_\mu + i(\theta^A+\alpha^A)Q_A + i(\bar{\theta}_{\dot{A}}+\bar{\alpha}_{\dot{A}})\bar{Q}^{\dot{A}}].

@@

(x^\mu, \theta^A, \bar{\theta}_{\dot{A}}) \to  (x^\mu + a^\mu -i\alpha^A\sigma^\mu_{A\dot{A}}\bar{\theta}^{\dot{A}} + i\theta^A\sigma^\mu_{A\dot{A}}\bar{\alpha}^{\dot{A}}, \theta^A + \alpha^A, \bar{\theta}_{\dot{A}} + \bar{\alpha}_{\dot{A}}),

@@

f_\pi(x^\mu, \theta^A, \bar{\theta}_{\dot{A}},a^\mu, \alpha^A, \bar{\alpha}_{\dot{A}}) =  (x^\mu + a^\mu -i\alpha^A\sigma^\mu{}_{A\dot{A}}\bar{\theta}^{\dot{A}} + i\theta^A\sigma^\mu{}_{A\dot{A}}\bar{\alpha}^{\dot{A}}, \theta^A + \alpha^A, \bar{\theta}_{\dot{A}} + \bar{\alpha}_{\dot{A}}).

@@

As a crucial by-product we can now write down a differential representation for the supersymmetry generators by applying the standard expression for the generators $X_i$ of a Lie algebra, given the composition functions $f_\pi$:
\[ iX_j = \frac{\partial f_\pi}{\partial a_j}\frac{\partial}{\partial z_\pi},\]
which gives us:
\begin{eqnarray}
iP_\mu &=& \partial_\mu \label{eq:diffrepP},\\
iQ_A &=& -i(\sigma^\mu\bar{\theta})_A\partial_\mu +\partial_A,\\
i\bar{Q}^{\dot{A}} &=& -i(\bar{\sigma}^\mu \theta)^{\dot{A}}\partial_\mu +\partial^{\dot{A}}.
\label{eq:diffrepQbar}
\end{eqnarray}
